Paper 1: Instrument development

### 2024-10-08 Rmd/Paper1.Rmd
Corrections

---
title:        "Paper 1: Instrument development"
author:       "Niklas Karlsen, OsloMet, Norway, e-mail: niklaska@oslomet.no"
date:         "2024-09-04"
bibliography: "../data/meta_data/references.bib"
csl:          "../scripts/university-of-gothenburg-apa-7th-edition-swedish-legislations.csl" # (source: https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html)
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true

@@

# add semester
data_pilot$semester                                        <- rep(0,16)
data_pilot$semester[data_pilot$studiested == "Institute6"] <- 6 
data_pilot$semester[data_pilot$studiested == "Institute4"] <- 4 
# Institute7/8, ?. semester 2/3?
data_pilot$semester[data_pilot$studiested == "Institute5"] <- 8

@@

```{r}
# load data
load(file="../data/processed_data/tpack-trelis_q_paper1_2023.Rdata")
```

@@

```{r remove_NMAR_TRELISQ}
# remove NMAR + NTNU (19)
CFA_TPACK_PST <- data_TRELIS_Q[-c(19,34,44,45,46,95,102),] 
```

>>>>

---
title:        "Paper 1: Instrument development"
author:       "Niklas Karlsen, OsloMet, Norway, e-mail: niklaska@oslomet.no"
date:         "2024-10-08"
bibliography: "../data/meta_data/references.bib"
csl:          "../scripts/university-of-gothenburg-apa-7th-edition-swedish-legislations.csl" # (source: https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html)
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true

@@

# add semester
data_pilot$semester                                        <- rep(0,16)
data_pilot$semester[data_pilot$studiested == "Institute6"] <- 6 
data_pilot$semester[data_pilot$studiested == "Institute4"] <- 4 
# Institute7/8, ?. år 2/3
data_pilot$semester[data_pilot$studiested == "Institute7"] <- 6 
data_pilot$semester[data_pilot$studiested == "Institute5"] <- 8

@@

```{r}
# load data
load(file="../data/processed_data/tpack-trelis_q_partial_2023-paper1.Rdata")
```

@@

```{r remove_NMAR_TRELISQ}
# remove NMAR (19)
CFA_TPACK_PST <- data_TRELIS_Q[-c(19,34,44,45,46,95,102),] 
```
